---
title: "HW6"
author: "Weize Sun"
date: "12/4/2021"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(broom)
library(dbplyr)
```


## Problem 1

### load and clean data
```{r}
birthweight = 
  read.csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace))
sum(is.na(birthweight))
```

There is no missing value in this dataset.


### Propose a regression model for birthweight

```{r}
birthweight_model = 
  lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + malform + menarche + mheight + momage + mrace + parity + pnumlbw + pnumsga + ppbmi + ppwt + smoken + wtgain, data = birthweight) 
broom::tidy(birthweight_model) %>% 
  knitr::kable(digits = 3)
```
### Describe my modeling process

I hypothesized all variables (besides bwt) to be predictors of this regression model. Then, I found that there are three predictors which give NA value, which are pnumlbw, pnumsga, and wtgain. Hence, I will not chose them as predictors.

Besides, I also found that p-value for fincome, frace, malform, menarche, mheight, momage, mrace(3&4), ppbmi and ppwt are greater than 0.05, and in this case we failed to reject the null hypothesis. Hence, I will also ombit these as predictors.

```{r}
better_model =
  lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + parity + smoken, data = birthweight)
broom::tidy(better_model) %>% 
  knitr::kable(digits = 3)
```



### Show a plot of model residuals against fitted values

```{r}
birthweight %>% 
  modelr::add_predictions(better_model) %>% 
  modelr::add_residuals(better_model) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = .3) + 
  geom_smooth(method = "lm", color = "red", se = FALSE) +
  labs(
    x = "Predicted values",
    y = "Residuals",
    title = "Residuals VS Predictions",
    caption = "data from p8105 website"
  )
```

### Compare my model to two others

```{r}
first_model = lm(bwt ~ blength + gaweeks, data = birthweight)
second_model = lm(bwt ~ bhead * blength * babysex, data = birthweight)
```

```{r}
cv_df =
  crossv_mc(birthweight, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
cv_df = 
  cv_df %>% 
  mutate(
    better_model = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + gaweeks + mrace + parity + smoken, data = .x)),
    first_model = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    second_model = map(train, ~gam(bwt ~ bhead * blength * babysex, data = as_tibble(.x)))) %>% 
  mutate(
    rmse_better_model = map2_dbl(better_model, test, ~rmse(model = .x, data = .y)),
    rmse_first_model = map2_dbl(first_model, test, ~rmse(model = .x, data = .y)),
    rmse_second_model = map2_dbl(second_model, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(
    title = "Comparison in terms of the cross-validated prediction error",
    caption = "data from p8105 website"
  )
```


